---
title: "marriage licence statistics for toronto"
author: 
  - Mingjin Zhan
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "This is the statistics of marriage licence statistics for toronto; looking for the relationship between data and number"
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```


# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....



# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point() +
  theme_minimal() +
  labs(x = "date", y = "number of marriage licenses")
```

From graph, the number of number of marriage licenses stays same for those years, but the number of date reduce from 2020.


\newpage


# References


